### 2017-10-22 TechnicalReport/article_3.tex
referencias usadas adecuadamente
Referencias y algunos items del marco teorico

\begin{description}
	\item[Document Clustering] Is the act of collecting similar documents into bins, where similarity is some function on a document. \ref{refer:1}
	\item[K-means Algorithm] Explanation
	\item[Jaccard Algorithm] Text \ref{refer:1}
\end{description}

@@

@@

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\phantomsection
\bibliographystyle{unsrt}
%\bibliography{sample}

\begin{itemize}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
	\item DISEÑO DE ALGORITMOS PARALELOS
	En el texto: (cs.buap, 2017)
	Bibliografía: cs.buap. (2017). Diseño de algoritmos paralelos.

	[online] Available at: https://www.cs.buap.mx/~mtovar/doc/ProgConc/ProgramacionParalela.pdf

	[Accessed 21 Oct. 2017].
	\item cs.fit.edu. (2017). \textit{A Comparison of Document Clustering Techniques.} [online] Available at: http://cs.fit.edu/~pkc/classes/ml-internet/papers/steinbach00tr.pdf [Accessed 18 Oct. 2017].
	\label{refer:1}
\end{itemize}

@@

>>>>

\begin{description}
	\item[K-means Algorithm] “The k-means method has been shown to be effective in producing good clustering results for many practical applications. However, a direct algorithm of k-means method requires time proportional to the product of number of patterns and number of clusters per iteration. This is computationally very expensive especially for large datasets.
	The number of iterations required can vary in a wide range from a few to several thousand depending on the number of patterns, number of clusters, and the input data distribution. Thus, a direct implementation of the k-means method can be computationally very intensive. This is especially true for typical data mining applications with large number of pattern vectors” \cite{K-means}.

	The algorithm is composed of the following steps:
	Place K points into the space represented by the objects that are being clustered. These points represent initial group centroids.

	Assign each object to the group that has the closest centroid.

	When all objects have been assigned, recalculate the positions of the K centroids.

	Repeat Steps 2 and 3 until the centroids no longer move. This produces a separation of the objects into groups from which the metric to be minimized can be calculated.

	figura sacada del mismo paper. \cite{K-means Algorithm}
	The number of K is determinate by the user and indicate the number of clusters.

	\item[Jaccard Algorithm] 
	“This is a particular notion of ‘similarity’: the similarity of sets by looking at the relative size of their intersection.
	The Jaccard similarity of sets S and T is |S instersected T |/|S union T |, that is, the ratio of the size of the intersection of S and T to the size of their union. We shall denote the Jaccard similarity of S and T by SIM(S, T ).  An important class of problems that Jaccard similarity addresses well is that of finding textually similar documents in a large corpus such as the Web or a collection of news articles. We should understand that the aspect of similarity we are looking at here is character-level similarity, not “similar meaning,” which requires us to examine the words in the documents and their uses.” \cite{jaccard_similarity}. 
	“To calculate the Jaccard dissimilarity the Jaccard similarity matrix is computed first and thereafter transformed.”\cite{jaccard_seudo}
	This can be reach following this steps:
	Count the number of members which are shared between both sets.
	Count the total number of members in both sets (shared and un-shared).
	Divide the number of shared members by the total number of members.
	Multiply the number you found in by 100. \cite{jaccard_steps}

\end{description}

@@

El diseño del algoritmo Jaccard que usamos lo sacamos de este sitio \cite{jaccard_seudo}.

@@

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\begin{thebibliography}{9}

\bibitem{K-means}
Alsabti, K., Ranka, S. and Singh, V. (2017). An Efficient K-Means Clustering Algorithm. [online] pp.1-2. \href{https://www.cs.utexas.edu/~kuipers/readings/Alsabti-hpdm-98.pdf}{Available clicking here} [Accessed 22 Oct. 2017].
\bibitem{K-means Algorithm}
Home.deib.polimi.it. (2017). Clustering - K-means. [online] \href{http://home.deib.polimi.it/matteucc/Clustering/tutorial_html/kmeans.html}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{jaccard_seudo}
Schulz, D. (2017). Jaccard similarity. [online] Code10.info. 
\href{http://www.code10.info/index.php?option=com_content&view=article&id=60:articlejaccard-similarity&catid=38:cat_coding_algorithms_data-similarity&Itemid=57}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{jaccard_similarity}

Standford University Infolab. (2017). \textit{Finding Similar Items}. [online] \href{http://infolab.stanford.edu/~ullman/mmds/ch3.pdf}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{jaccard_steps} 
Statistics How To. (2017). Jaccard Index / Similarity Coefficient. [online] [Accessed 22 Oct. 2017].
\href{http://www.statisticshowto.com/jaccard-index/}{Available clicking here}  [Accessed 22 Oct. 2017].

\bibitem{DISENO DE ALGORITMOS PARALELOS}
En el texto: (cs.buap, 2017)
Bibliografía: cs.buap. (2017). Diseño de algoritmos paralelos. [online] \href{https://www.cs.buap.mx/~mtovar/doc/ProgConc/ProgramacionParalela.pdf}{Available clicking here} [Accessed 21 Oct. 2017].
\item cs.fit.edu. (2017). \textit{A Comparison of Document Clustering Techniques.} [online]  \href{http://cs.fit.edu/~pkc/classes/ml-internet/papers/steinbach00tr.pdf}{Available clicking here} [Accessed 18 Oct. 2017].

\end{thebibliography}

@@

% no BORRAR:
%\begin{verbatim}
%CODE HERE
%\end{verbatim}
